\section{Running tests}
\label{sec:running-tests}

\subsection{Running single tests}
\label{sec:running-single}

\begin{enumerate}
\item From the main page open \textit{Functional} or \textit{Benchmarks} tab.
\item Click on the test name.
\item Click on \textit{Run test now}.
\end{enumerate}

Here you can set test run parameters.
The most relevant are:

\begin{description}
\item[Device:] Choose a target the test will be run on.
\item[Reboot:] If checked target device will be rebooted before running test.
\item[Rebuild:] Rebuild\footnote{Some tests require rebuilding if their parameters were changed.} the test.
\item[TESTPLAN:] (optional) Derive test parameters from test specifications from chose testplan. For testplans see [\ref{sec:testplans}]
\end{description}

Press \textit{Run test} button. The test is scheduled for running. If no tests are executed on target it will be run immediately. It will appear in the left frame name \textit{Test run history}. There you can see all this specific test results (including currenlty running one). They can be of a few types:
\begin{description}
\item[Solid green circle:] The test has been successefully run.
\item [Solid red circle:] The test has failed.
\item [Flashing circle:] The test is currently running.
\end{description}

If you point mouse over the date of test run the pop-up menu appears from where you can go to \textit{Console output}. There you can view the complete log of test run.

\subsection{Running a group of tests}
\label{sec:running-batch}

\begin{enumerate}
\item From the main page open \textit{Batch runs}.
\item Click on \textit{Run SELECTED tests on SELECTED targets}.
\item Click on \textit{Run test now}.
\item Choose a target\footnote{Reports generation is implemented only for the first target selected and only for Run SELECTED tests on SELECTED batch run}
\item Mark tests/benchmarks you would like to run.
\item Enter test plan to \texttt{TESTPLAN} variable. Test plan is mandatory for batch runs.
\item Click on \textit{Run test} button.
\end{enumerate}

The batch test run is scheduled for running on target. On the test page there is a list of running tests (their statuses are the same as in [\ref{sec:running-single}]).

When batch run is finished you can view generated PDF report.

\subsection{Viewing PDF reports}
\label{sec:view-pdf}
\begin{enumerate}
 \item From the batch test run page click on \textit{Workspace link}
\item Click on
  \href{http://localhost:8090/view/batch\%20runs/job/Run\%20SELECTED\%20tests\%20on\%20SELECTED\%20targets/ws/pdf\_reports/}{pdf\_reports} folder.
\item Click the bottommost pdf file. \\ It has \texttt{<target>.<date>.<testrun>.json.xml.pdf} format.

\end{enumerate}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "fuego-guide"
%%% End: 
